---
title: "Supplementary material for Consumers' preferences for commons-based and open-source produce: A discrete choice experiment with directional information manipulations."
author: " Lea Kliem and Julian Sagebiel"
date: "13/04/2022"
output:
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---


This script analyses the data collected from the main survey of the paper "Consumers' preferences for commons-based and open-source tomatoes: A discrete choice experiment". It includes the second pilot, but not the first pilot. The first pilot cannot be used because attributes etc changed.

The script includes all relevant steps from preparation of raw data to final models. Readers can use the data and code.

The preregistration can be found here https://aspredicted.org/blind.php?x=K3X_S4Z


# Prepare Data


<details>
  <summary>Prepare Data</summary>


First, load packages and user written functions.

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library("flextable")
library("dplyr")          
library("evd")           
library("boot")
library("apollo")
library("sjlabelled")
library("readxl")
library("httr")
library("ggplot2")
library("tidyr")
library("magrittr")
library("psych")
library("kableExtra")
library("tidylog")
library("texreg")



source("helpfunctions.R")


No_draws =1500

```

```{r}
rightseeds_live_pages <- read_excel("data/mainstudy/rightseeds_live_pages.xlsx")
```



```{r prep}


# read in all datasets and merge

dce_data <- bind_rows(read_excel("data/mainstudy/rightseeds_live_dce_gg.xlsx"), read_excel("data/mainstudy/rightseeds_live_dce_os.xlsx") ,.id = "gg") %>%  ## gg: 1= gg 2 = oc
  left_join(read_excel("data/mainstudy/rightseeds_live_covariates.xlsx"), by ="RID") #%>% 
  #select(1:18, info_text)


dce_dict<- read_excel("data/mainstudy/rightseeds_live_dce_os.xlsx" , sheet = "dictionary")
cov_dict<- read_excel("data/mainstudy/rightseeds_live_covariates.xlsx" , sheet = "dictionary")


  

  # Merge with time stamp data to identify speeders 
  
  database2 <-  dce_data%>% 
   #filter(!is.na(pref1)) %>% 
    filter(!is.na(q28), q8_16==4|q8_16 %in% c(4,6) ) %>%   
left_join(rightseeds_live_pages, by="RID") %>% 
  mutate(duration_lastp = PAGE_SUBMIT_30-PAGE_DISPLAY_30 ,
         duration_lastp_imputed= if_else(is.na(duration_lastp), mean(duration_lastp, na.rm=TRUE),duration_lastp ),
         DURATION_ALL= PAGE_DISPLAY_30+duration_lastp_imputed,
         threshold=1/3*mean(DURATION_ALL)) %>% 
  filter(DURATION_ALL>threshold)  %>% 
     mutate(Female=case_when(q20==2 ~ 1,   TRUE ~0) , Female_s =as.numeric(scale(Female, scale=FALSE)),
            Age_s = as.numeric(scale(q21, scale=FALSE)),
            HigherEdu=case_when(q26_new %in% c(1,2,3,8) ~ 0,   TRUE ~1) , HigherEdu_s =as.numeric(scale(HigherEdu, scale=FALSE)), # higher education as Meisterausbildung und höher
            Income=case_when(q28 ==7 ~ mean(q28,na.rm=TRUE),   TRUE ~q28) , Income_s =as.numeric(scale(Income, scale=FALSE)),
       across(matches("._x[4]$ " ) , ~ .x - 1 ) ,
                        oc = as.numeric(gg)-1 ,  # 0= commons 1 =open source
                        winter =as.numeric(jahreszeit)-1 ,  # 0=summer 1 = winter
           across(matches("._x1$") ,  ~ recode(  .x ,`1` = 0.99,`2` = 1.49  , `3` = 1.99 , `4` = 2.49 , `5` = 2.99 , `6` = 3.49 , `7` = 3.99 , `8` = 4.99 , .default =99999)) ,
           a1_EUBIO = a1_x2==2, a1_BIOVER = a1_x2==3 , a2_EUBIO = a2_x2==2, a2_BIOVER = a2_x2==3 ,
           a1_REG = a1_x3==1, a1_DE = a1_x3==2 , a1_ESP = a1_x3==3 , a1_MAR = a1_x3==4 ,a2_REG = a2_x3==1,  a2_DE = a2_x3==2 ,  a2_ESP = a2_x3==3 , a2_MAR = a2_x3==4
    )   %>% 
    as.data.frame()
 table(database2$gg) 
 
 length(unique(database2$RID))

```
</details>



# Descriptive Analysis

<details>
  <summary>Descriptive Analysis</summary>

We look at the frequencies of attribute levels and correlations between attributes. This should confirm that the design is balanced and orthogonal.

```{r design, eval=TRUE}

table(database2$DESIGN_ROW)
  
  ## For all respondents
  table(database2$a1_x1)
  table(database2$a1_x2)
  table(database2$a1_x3)
  table(database2$a1_x4)

  
  #Only for the first respondents
  table(database2$a1_x1[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x2[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x3[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x4[unique(database2$DESIGN_ROW)], useNA = "always")

  

  ## Over all observations
  cor(database2[, 6:15])
  
  ## Only design
  cor(database2[(unique(database2$DESIGN_ROW)), 6:15])
  
  
  
  table(database2$pref1)
  
  #as probabilities
  
  table(database2$pref1)/length(database2$pref1)
  
```

 We plot the choice probabilities conditional on the attribute level. It should confirm the direction and magnitute of our estimates.  


```{r choiceprobs, eval=TRUE}  
    
  barplot(prop.table(table(database2$pref1)), ylim = c(0,1), col=c("cyan1", "cyan3", "darkcyan"))
  
  
  aggregate(as.numeric(pref1)==1 ~ a1_x1 , data=database2 , mean)
  aggregate(as.numeric(pref1)==2 ~ a2_x1 , data=database2 , mean)

  plot(aggregate(as.numeric(pref1)==1 ~ a1_x1 , data=database2 , mean), type="l")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x1 , data=database2 , mean), type="l")
  
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x2 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x2 , data=database2 , mean), type="o")
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x3 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x3 , data=database2 , mean), type="o")
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x4 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x4 , data=database2 , mean), type="o")
  

  


```


The following table shows how often respondents have chosen which alternatives. For example the 151 in column Alt1 means that 151 respondents have chosen alternative 1 only once in all nine choice situations. 

```{r individualswitching, eval =TRUE}
ind_switch <- database2 %>% 
  group_by(RID, pref1) %>% 
  summarise(n = n()) %>% 
  ungroup %>% 
  group_by(n, pref1) %>% 
  summarise(freq=n()) %>% 
  arrange(pref1) %>% 
  spread(pref1,freq,fill = 0) %>% 
  rename(nchosen=n, Alt1 =2 , Alt2 = 3 , Optout = 4)

kable(ind_switch) %>%  kable_classic_2(full_width = T)
```
</details>

#  Logit Models

<details>
  <summary>Logit Models</summary>

The following chunk will estimate the logit models. It is set to `eval = FALSE` as default because estimation takes long. To replicate the analysis, one has to run this chunk only once. The files will be saved as R objects in the local folder.

```{r estimate logitmodels, eval=FALSE}

source("scripts/clogitmodels.R")
source("scripts/mixlogitmodels.R")
source("scripts/mixedlogit_scriptinteractions.R")

delfiles <- dir(path="modeloutput/",  pattern=".csv" ,full.names = T)

file.remove(delfiles)

```


The following chunk is also set to `eval=FALSE`. It estimates Latent Class models with 2 to 6 classes.
```{r estimate lcmodels, eval = FALSE}

map(2:6, function(x) {n_classes <<- x  
                       source("scripts/lcmodels/lc_body.R")
} )


```



```{r readinsavedWTPModel, eval=T, results='hide'}


delfiles <- dir(path="modeloutput/",  pattern="OLD" ,full.names = T,recursive = TRUE)

file.remove(delfiles)


  



modelpath <-list.files(path = "modeloutput/WTPSpace/",pattern = "rds$" , full.names = TRUE, recursive = TRUE)
models_tex <- list()
models <- list()


for (name in modelpath) {

t <- readRDS(name)
#twtp <- wtp("b_cost",attr = names(t$estimate) , modelname=t) # only relevant if models are not estimated in WTP space

models[[t$apollo_control$modelName]] <-t
models_tex[[t$apollo_control$modelName]] <-quicktexregapollo(t)

}

rm(t, name, modelpath)
  
 

```



```{r readinsavedPrefModel, eval=T, results='hide'}







  



modelpath <-list.files(path = "modeloutput/mixlogit_prefspace/",pattern = "rds$" , full.names = TRUE)
models_tex <- list()
models <- list()


for (name in modelpath) {

t <- readRDS(name)
twtp <- wtp("cost",attr = names(t$estimate) , modelname=t) # only relevant if models are not estimated in WTP space

models[[t$apollo_control$modelName]] <-t
models_tex[[t$apollo_control$modelName]] <-quicktexregapollo(t)
clmodelsWTP[[t$apollo_control$modelName]]<-twtp
clmodelsWTP_tex[[t$apollo_control$modelName]] <- quicktexregapollo(model=t,wtpest = twtp)

}

rm(t,twtp, name, modelpath)
  
 

```


This chunk loads saved latent class models and prepares tables with coefficients and willingness to pay.

```{r loadlcmodels , eval=TRUE, results='hide'}

delfiles <- dir(path="modeloutput/lclogit",  pattern="OLD" ,full.names = T)

file.remove(delfiles)

modelpath <-list.files(path = "modeloutput/lclogit/",pattern = "*.rds" , full.names = TRUE)
lcmodels_tex <- list()
lcmodels     <- list()
lcmodelsWTP  <- list()
lcmodelsWTP_tex <- list()

for (name in modelpath) {

  t <- readRDS(name)

  twtp <- wtp_lc(modelname=t)
  
  lcmodels[[t$apollo_control$modelName]]     <-t
  lcmodels_tex[[t$apollo_control$modelName]] <-quicktexregapollo(t)
  lcmodelsWTP[[t$apollo_control$modelName]]  <- twtp

 for (class in 1:(length(t$LL0)-1)) {

    cl <- twtp[[class]]
    clet <- intToUtf8(96+class)



 lcmodelsWTP_tex[[t$apollo_control$modelName]][[paste0("Class", class)]] <-  quicktexregapollo(t,cl)

}


}

rm(t,twtp, name, modelpath)

```
</details>

# Appendix A: Individual Willingness to pay values

<details>
  <summary>Appendix A: Individual Willingness to pay values</summary>

```{r individual wtp}
library(purrr)
library(ggpubr)

# Read in individual WTP estimates 
individualWTP_notext <- readRDS("modeloutput/Individual_wtp/individualWTP_notext.rds")
individualWTP_ind <- readRDS("modeloutput/Individual_wtp/individualWTP_ind.rds")
individualWTP_env <- readRDS("modeloutput/Individual_wtp/individualWTP_env.rds")

# Define a function that takes a variable name as input and returns a ggplot object
plot_wtp <- function(var_name) {
  ggplot(data.frame(x = individualWTP_env[[var_name]]$post.mean), aes(x = x, col="Env")) +
    geom_density() +
    geom_density(data = data.frame(x = individualWTP_ind[[var_name]]$post.mean), aes(x = x, col="Ind")) +
    geom_density(data = data.frame(x = individualWTP_notext[[var_name]]$post.mean), aes(x = x, col="Notext")) +
    ggtitle(var_name) +
    xlab("WTP") +
    ylab("Density") +
    labs(col="Treatment") +
    theme(legend.position = c(0.15, 0.85))
}

# apply the function to each variable in individualWTP data frames
plot_list <- map(names(individualWTP_env), plot_wtp)

# plot densities 
ggarrange(plotlist = plot_list, nrow = 2, ncol = 4, common.legend = T, legend = "bottom")

```

```{r, include=F}
ggsave("Figure_revision/individualWTP.png", width = 16, height =9, dpi="print")
```
</details>

# Appendix B: Models separated by season

<details>
  <summary>Appendix B: Models separated by season</summary>

```{r, message=F}
library(tibble)
library(reshape2)
```


```{r season, eval=T, out.width="120%"}

mxl_season_compare <- as.data.frame(models$mixlog_season_winter$estimate)
mxl_season_compare[2] <- as.data.frame(models$mixlog_season_summer$estimate)

alpha = 0.1 # set confidence level 

mxl_season_compare$margin_of_error_w <- qnorm(1-alpha/2)*models$mixlog_season_winter$robse
mxl_season_compare$margin_of_error_s <- qnorm(1-alpha/2)*models$mixlog_season_summer$robse

mxl_season_compare <- rownames_to_column(mxl_season_compare, "Coefficent")

colnames(mxl_season_compare) <- c("Coefficent", "Estimate_winter", "Estimate_summer", "Margin_of_error_winter",
                                "Margin_of_error_summer")


mxl_melt_season <- melt(mxl_season_compare[1:3], id = "Coefficent")
mxl_melt_season$ME <- mxl_season_compare$Margin_of_error_winter
mxl_melt_season$ME[22:42] <- mxl_season_compare$Margin_of_error_summer


ggplot(data=mxl_melt_season, aes(x=Coefficent, y=abs(value), fill=variable)) +
  geom_bar(stat="identity",  position='dodge', width = 0.9) +
  geom_errorbar(aes(x=Coefficent, ymin=abs(value)-ME, ymax=abs(value)+ME), width=0.3, position=position_dodge(0.8)) +
  ylab("Absolute Value") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_brewer(palette = 7, labels = c("Winter", "Summer"), name="Season") +
  theme(legend.position = c(0.9, 0.85))

```

```{r, results='asis'}
mixmodelsWTP_tex <- models_tex[c("mixlog_season_winter", "mixlog_season_summer") ]

htmlreg(l = mixmodelsWTP_tex  ,
        custom.model.names = c("Winter", "Summer") ,  caption = "Results for mixed logit model for the two different seasons" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE)
```


# Appendix C: Models separated by Tomato Type

<details>
  <summary>Appendix C: Models separated by Tomato Type</summary>

```{r tomato_type, eval=T, out.width="120%"}


mxl_tomato_compare <- as.data.frame(models$mixlog_small_tomato$estimate)
mxl_tomato_compare[2] <- as.data.frame(models$mixlog_big_tomato$estimate)

alpha = 0.1 # set confidence level 

mxl_tomato_compare$margin_of_error_w <- qnorm(1-alpha/2)*models$mixlog_small_tomato$robse
mxl_tomato_compare$margin_of_error_s <- qnorm(1-alpha/2)*models$mixlog_big_tomato$robse

mxl_tomato_compare <- rownames_to_column(mxl_tomato_compare, "Coefficent")

colnames(mxl_tomato_compare) <- c("Coefficent", "Estimate_small", "Estimate_big", "Margin_of_error_small",
                                "Margin_of_error_big")


mxl_melt_tomato <- melt(mxl_tomato_compare[1:3], id = "Coefficent")
mxl_melt_tomato$ME <- mxl_tomato_compare$Margin_of_error_small
mxl_melt_tomato$ME[23:44] <- mxl_tomato_compare$Margin_of_error_big


ggplot(data=mxl_melt_tomato, aes(x=Coefficent, y=abs(value), fill=variable)) +
  geom_bar(stat="identity",  position='dodge', width = 0.9) +
  geom_errorbar(aes(x=Coefficent, ymin=abs(value)-ME, ymax=abs(value)+ME), width=0.3, position=position_dodge(0.8)) +
  ylab("Absolute Value") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_brewer(palette = 13, labels = c("Small", "Big"), name="Tomato") +
  theme(legend.position = c(0.9, 0.85))

```

```{r, include=F}
ggsave("Figure_revision/tomato.png", dpi = "print",  width = 10.5, height = 7.5)
```


```{r, results='asis'}
mixmodelsWTP_tex <- models_tex[c("mixlog_small_tomato", "mixlog_big_tomato") ]

htmlreg(l = mixmodelsWTP_tex  ,
        custom.model.names = c("Small Tomato", "Big Tomato") ,  caption = "Results for mixed logit model for the two different tomato types" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE)
```
</details>

# Appendix D: Latent Class Analysis

<details>
  <summary>Appendix D: Latent Class Analysis</summary>

```{r lc wtp , results="asis", include=TRUE, eval=TRUE} 

for(clno in names(lcmodelsWTP_tex)){

nclasses <-length(lcmodels[[clno]]$LL0)-1  
clshare <- round(100*sapply(lcmodels[[clno]][["unconditionals"]][["pi_values"]],mean), digits = 1  ) 
modelnames <- sprintf("Class %d",seq(1:nclasses ))

print(
htmlreg(lcmodelsWTP_tex[[clno]] ,
       single.row = TRUE ,
      # custom.model.names = paste0("\\specialcell{",modelnames, "\\\\  (" , clshare , "\\%)}") ,
       caption = paste0("WTP values of latent class model with " ,nclasses, " classes" ),
       #groups = list("WTP"=1:6, "Membership" = 7:length(lcmodelsWTP_tex[["lc2cl"]][["Class2"]]@coef.names) )
)
)
}       
 

#  custom.coef.names = rep(c("ASC", "MANUFEU" , "MANUFSWE", "CULTEU", "CULTSWE", "ECO") ,times=nclasses  ),    

```


# Appendix E: Conditional Logit models

<details>
  <summary>Appendix E: Conditional Logit models</summary>

```{r clogittables, results='asis'}

clmodelsWTP_tex <- models_tex[c("clog_allsamples",  "clog_split_notext" , "clog_split_env"  ,  "clog_split_ind") ]

htmlreg(l = clmodelsWTP_tex , 
        custom.model.names = c("Full Sample", "No Text", "Environment" , "Industry") ,  caption = "Results from Infotext Splits" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )


```
</details>

# Appendix F: Models used in paper

<details>
  <summary>Appendix F: Models used in paper</summary>

```{r resultsmixedlogit, results='asis'}

mixmodelsWTP_tex <- models_tex[c("mixlog_allsamples",  "mixlog_split_notext" , "mixlog_split_env"  ,  "mixlog_split_ind") ]

htmlreg(l = mixmodelsWTP_tex  ,
        custom.model.names = c("Full Sample", "No Text", "Environment" , "Industry") ,  caption = "Results from Infotext Splits with mixed logit models" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )


```


# Appendix G: Pooled Model with Information Splits

<details>
  <summary>Appendix G: Pooled Model with Information Splits</summary>

```{r resultsmixedsplitint, results='asis'}


mixlogit_scriptint_tex <- models_tex[["mixlog_scriptint"]]


splitit <-function (select, listobj) {
  
  t<- listobj
  
cells <-grep(select,t@coef.names)  
  
t@coef.names <- t@coef.names[cells]
t@coef <- t@coef[cells]
t@se <- t@se[cells]
t@pvalues <- t@pvalues[cells]
return(t)  

}


intmodel_split <- purrr::map(c("mean","sd", "Info2","Info3"), splitit,mixlogit_scriptint_tex)

# change coefficient names for output table 
intmodel_split <- map(intmodel_split, ~ {
  if(length(.x@coef.names) > 7) {
    .x@coef.names <- c("asc", "eubio", "biover", "reg", "de", "esp", "eigent", "cost")
  } else {
    .x@coef.names <- c("asc", "eubio", "biover", "reg", "de", "esp", "eigent")
  }
  .x
})


htmlreg(l = c(intmodel_split[1], remGOF(intmodel_split[2:4])) ,  custom.model.names = c("Mean", "Standard deviation", "Interaction Info 2", "Interaction Info 3"),
          caption = "Results from mixed logit model with interactions of information treatments" , single.row = T  , 
        
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )

```
</details>

# Appendix H: Z-Tests for differences in parameters between information splits

<details>
  <summary>Appendix H: Z-Tests for differences in parameters between information splits</summary>

```{r ztest}



z.envXind <- apollo_ztest(models[["mixlog_split_env"]],models[["mixlog_split_ind"]])

z.envXnotext <- apollo_ztest(models[["mixlog_split_env"]],models[["mixlog_split_notext"]])


z.notextXind <-apollo_ztest(models[["mixlog_split_notext"]],models[["mixlog_split_ind"]])


# apollo_ztest(models[["clog_split_env"]],models[["clog_split_ind"]])
# 
# apollo_ztest(models[["clog_split_env"]],models[["clog_split_notext"]])
# 
# 
# apollo_ztest(models[["clog_split_notext"]],models[["clog_split_ind"]])


ztest.pvals <- z.envXind %>% 
  tibble::rownames_to_column() %>% 
  bind_cols(z.envXnotext,z.notextXind ) %>% 
  select(Attribute = rowname,EnvXind = p_value...9 , EnvXnotext = p_value...17, notextXind = p_value...25)


kable(ztest.pvals) %>% kable_styling()

#flextable(ztest.pvals,) %>% colformat_double(digits = 3) %>% save_as_docx(path = "tables/ztest.docx")


```
</details>


# Appendix I: Model with familiarity interactions

<details>
  <summary>Appendix I: Model with familiarity interactions</summary>

```{r fam int, results='asis'}

mixmodelsWTP_tex <- models_tex[c("mixlog_int_tab4")]

htmlreg(l = mixmodelsWTP_tex  ,
        custom.model.names = c("Familiarity interactions") ,  caption = "Results from familiarityinteractions model" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )


```

</details>

# Appendix J: Models in preference space 

<details>
  <summary>Appendix J: Models in preference space</summary>

```{r pref space, results='asis'}

mixmodelsWTP_tex <- models_tex[c("mixlog_pref_space", "mixlog_fix_price")]

htmlreg(l = mixmodelsWTP_tex  ,
        custom.model.names = c("Log-normal price", "Fixed price") ,  caption = "Results from models in preference space" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )


``` 
  
</details>