---
title: "Supplementary material for Consumers' preferences for commons-based and open-source tomatoes: A discrete choice experiment Code for Analysis"
author: " Lea Kliem and Julian Sagebiel"
date: "07/06/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


This script analyses the data collected from the main survey of the paper "Consumers' preferences for commons-based and open-source tomatoes: A discrete choice experiment". It includes the second pilot, but not the first pilot. The first pilot cannot be used because attributes etc changed.

The script includes all relevant steps from preparation of raw data to final models. Readers can use the data and code.

The preregistration can be found here https://aspredicted.org/blind.php?x=K3X_S4Z




# Prepare data


First, load packages and user written functions.

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

library("flextable")
library("dplyr")          
library("evd")           
library("boot")
library("apollo")
library("sjlabelled")
library("readxl")
library("httr")
library("ggplot2")
library("tidyr")
library("magrittr")
library("psych")
library("kableExtra")
library("tidylog")
library("texreg")



source("helpfunctions.R")

```

```{r}
rightseeds_live_pages <- read_excel("data/mainstudy/rightseeds_live_pages.xlsx")
```



no_text

text1

text2


```{r prep}

dce_data <- bind_rows(read_excel("data/mainstudy/rightseeds_live_dce_gg.xlsx"), read_excel("data/mainstudy/rightseeds_live_dce_os.xlsx") ,.id = "gg") %>%  ## gg: 1= gg 2 = oc
  left_join(read_excel("data/mainstudy/rightseeds_live_covariates.xlsx"), by ="RID") #%>% 
  #select(1:18, info_text)


dce_dict<- read_excel("data/mainstudy/rightseeds_live_dce_os.xlsx" , sheet = "dictionary")
cov_dict<- read_excel("data/mainstudy/rightseeds_live_covariates.xlsx" , sheet = "dictionary")


  

  # Get data from SurveyEngine - import as xls
  
  database2 <-  dce_data%>% 
   #filter(!is.na(pref1)) %>% 
    filter(!is.na(q28), q8_16==4|q8_16 %in% c(4,6) ) %>%   ## q28 ==NA, q8_16==4 or q8_16 == weiss nicht, respondents who took too little time
left_join(rightseeds_live_pages, by="RID") %>% 
  mutate(duration_lastp = PAGE_SUBMIT_30-PAGE_DISPLAY_30 ,
         duration_lastp_imputed= if_else(is.na(duration_lastp), mean(duration_lastp, na.rm=TRUE),duration_lastp ),
         DURATION_ALL= PAGE_DISPLAY_30+duration_lastp_imputed,
         threshold=1/3*mean(DURATION_ALL)) %>% 
  filter(DURATION_ALL>threshold)  %>% 
     mutate(Female=case_when(q20==2 ~ 1,   TRUE ~0) , Female_s =as.numeric(scale(Female, scale=FALSE)),
            Age_s = as.numeric(scale(q21, scale=FALSE)),
            HigherEdu=case_when(q26_new %in% c(1,2,3,8) ~ 0,   TRUE ~1) , HigherEdu_s =as.numeric(scale(HigherEdu, scale=FALSE)), # higher education as Meisterausbildung und höher
            Income=case_when(q28 ==7 ~ mean(q28,na.rm=TRUE),   TRUE ~q28) , Income_s =as.numeric(scale(Income, scale=FALSE)),
       across(matches("._x[4]$ " ) , ~ .x - 1 ) ,
                        oc = as.numeric(gg)-1 ,  # 0= gemeingut 1 =open source
                        winter =as.numeric(jahreszeit)-1 ,  # 0=sommer 1 = winter
           across(matches("._x1$") ,  ~ recode(  .x ,`1` = 0.99,`2` = 1.49  , `3` = 1.99 , `4` = 2.49 , `5` = 2.99 , `6` = 3.49 , `7` = 3.99 , `8` = 4.99 , .default =99999)) ,
           a1_EUBIO = a1_x2==2, a1_BIOVER = a1_x2==3 , a2_EUBIO = a2_x2==2, a2_BIOVER = a2_x2==3 ,
           a1_REG = a1_x3==1, a1_DE = a1_x3==2 , a1_ESP = a1_x3==3 , a1_MAR = a1_x3==4 ,a2_REG = a2_x3==1,  a2_DE = a2_x3==2 ,  a2_ESP = a2_x3==3 , a2_MAR = a2_x3==4
    )   %>% 
    as.data.frame()
 table(database2$gg) 
 
 length(unique(database2$RID))
 
 #write.csv(as.character(unique(database2$RID)), "selectedrespondents.csv" , row.names = FALSE, col.names = "RID")
 
```

```{r , eval=FALSE}
#Distribution of Blocks
database2 %>% distinct(RID, .keep_all = TRUE) %>%  select(matches("block")) %>% pivot_longer(1:6, "split","dd") %>% filter(!is.na(value))%>% group_by(split, value) %>%  summarise(n=n()) %>% pivot_wider(names_from = split, values_from = n)


 table(database2$gg) 
```


```{r desc, eval=FALSE}

table(database2$DESIGN_ROW)
  
  ## For all respondents
  table(database2$a1_x1)
  table(database2$a1_x2)
  table(database2$a1_x3)
  table(database2$a1_x4)

  
  #Only for the first respondents
  table(database2$a1_x1[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x2[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x3[unique(database2$DESIGN_ROW)], useNA = "always")
  table(database2$a1_x4[unique(database2$DESIGN_ROW)], useNA = "always")

  

  ## Over all observations
  cor(database2[, 6:15])
  
  ## Only design
  cor(database2[(unique(database2$DESIGN_ROW)), 6:15])
  
  
  
  table(database2$pref1)
  
  #as probabilities
  
  table(database2$pref1)/length(database2$pref1)
  
  
  barplot(prop.table(table(database2$pref1)), ylim = c(0,1))
  
  
  aggregate(as.numeric(pref1)==1 ~ a1_x1 , data=database2 , mean)
  aggregate(as.numeric(pref1)==2 ~ a2_x1 , data=database2 , mean)

  plot(aggregate(as.numeric(pref1)==1 ~ a1_x1 , data=database2 , mean), type="l")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x1 , data=database2 , mean), type="l")
  
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x2 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x2 , data=database2 , mean), type="o")
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x3 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x3 , data=database2 , mean), type="o")
  
  plot(aggregate(as.numeric(pref1)==1 ~ a1_x4 , data=database2 , mean), type="o")
  plot(aggregate(as.numeric(pref1)==2 ~ a2_x4 , data=database2 , mean), type="o")
  

  


```


```{r individualswitching, eval =FALSE}
ind_switch <- database2 %>% 
  group_by(RID, pref1) %>% 
  summarise(n = n()) %>% 
  ungroup %>% 
  group_by(n, pref1) %>% 
  summarise(freq=n()) %>% 
  arrange(pref1) %>% 
  spread(pref1,freq,fill = 0) %>% 
  rename(nchosen=n, Alt1 =2 , Alt2 = 3 , Optout = 4)

kable(ind_switch) %>%  kable_classic_2(full_width = T)
```




#  Logit models

```{r estimate logitmodels, eval=T}

source("scripts/clogitmodels.R")
source("scripts/mixlogitmodels.R")
source("scripts/mixedlogit_scriptinteractions.R")

delfiles <- dir(path="modeloutput/",  pattern=".csv" ,full.names = T)

file.remove(delfiles)

```

```{r readinsavedModel, eval=T}


delfiles <- dir(path="modeloutput/",  pattern="OLD" ,full.names = T)

file.remove(delfiles)


  



modelpath <-list.files(path = "modeloutput/",pattern = "rds$" , full.names = TRUE)
models_tex <- list()
models <- list()


for (name in modelpath) {

t <- readRDS(name)
#twtp <- wtp("b_cost",attr = names(t$estimate) , modelname=t) # only relevant if models are not estimated in WTP space

models[[t$apollo_control$modelName]] <-t
models_tex[[t$apollo_control$modelName]] <-quicktexregapollo(t)


}

rm(t,twtp, name, modelpath)
  
 

```

```{r individual wtp}
library(purrr)
library(ggpubr)

# Read in individual WTP estimates 
individualWTP_notext <- readRDS("modeloutput/Individual_wtp/individualWTP_notext.rds")
individualWTP_ind <- readRDS("modeloutput/Individual_wtp/individualWTP_ind.rds")
individualWTP_env <- readRDS("modeloutput/Individual_wtp/individualWTP_env.rds")

# Define a function that takes a variable name as input and returns a ggplot object
plot_wtp <- function(var_name) {
  ggplot(data.frame(x = individualWTP_env[[var_name]]$post.mean), aes(x = x, col="Env")) +
    geom_density() +
    geom_density(data = data.frame(x = individualWTP_ind[[var_name]]$post.mean), aes(x = x, col="Ind")) +
    geom_density(data = data.frame(x = individualWTP_notext[[var_name]]$post.mean), aes(x = x, col="Notext")) +
    ggtitle(var_name) +
    xlab("WTP") +
    ylab("Density") +
    labs(col="Treatment") +
    theme(legend.position = c(0.15, 0.85))
}

# apply the function to each variable in individualWTP data frames
plot_list <- map(names(individualWTP_env), plot_wtp)

# plot densities 
ggarrange(plotlist = plot_list, nrow = 2, ncol = 4, common.legend = T, legend = "bottom")
ggsave("Figure_revision/individualWTP.png", width = 16, height =9, dpi="print")
```

```{r season, eval=T}
library(tibble)
library(reshape2)

mxl_season_compare <- as.data.frame(models$mixlog_season_winter$estimate)
mxl_season_compare[2] <- as.data.frame(models$mixlog_season_summer$estimate)

alpha = 0.1 # set confidence level 

mxl_season_compare$margin_of_error_w <- qnorm(1-alpha/2)*models$mixlog_season_winter$robse
mxl_season_compare$margin_of_error_s <- qnorm(1-alpha/2)*models$mixlog_season_summer$robse

mxl_season_compare <- rownames_to_column(mxl_season_compare, "Coefficent")

colnames(mxl_season_compare) <- c("Coefficent", "Estimate_winter", "Estimate_summer", "Margin_of_error_winter",
                                "Margin_of_error_summer")


mxl_melt_season <- melt(mxl_season_compare[1:3], id = "Coefficent")
mxl_melt_season$ME <- mxl_season_compare$Margin_of_error_winter
mxl_melt_season$ME[22:42] <- mxl_season_compare$Margin_of_error_summer


ggplot(data=mxl_melt_season, aes(x=Coefficent, y=abs(value), fill=variable)) +
  geom_bar(stat="identity",  position='dodge', width = 0.9) +
  geom_errorbar(aes(x=Coefficent, ymin=abs(value)-ME, ymax=abs(value)+ME), width=0.3, position=position_dodge(0.8)) +
  ylab("Absolute Value") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_brewer(palette = 7, labels = c("Winter", "Summer"), name="Season") +
  theme(legend.position = c(0.9, 0.85))

ggsave("Figure_revision/season.png", dpi = "print",  width = 10.5, height = 7.5)

```


```{r tomato_type, eval=T}


mxl_tomato_compare <- as.data.frame(models$mixlog_small_tomato$estimate)
mxl_tomato_compare[2] <- as.data.frame(models$mixlog_big_tomato$estimate)

alpha = 0.1 # set confidence level 

mxl_tomato_compare$margin_of_error_w <- qnorm(1-alpha/2)*models$mixlog_small_tomato$robse
mxl_tomato_compare$margin_of_error_s <- qnorm(1-alpha/2)*models$mixlog_big_tomato$robse

mxl_tomato_compare <- rownames_to_column(mxl_tomato_compare, "Coefficent")

colnames(mxl_tomato_compare) <- c("Coefficent", "Estimate_small", "Estimate_big", "Margin_of_error_small",
                                "Margin_of_error_big")


mxl_melt_tomato <- melt(mxl_tomato_compare[1:3], id = "Coefficent")
mxl_melt_tomato$ME <- mxl_tomato_compare$Margin_of_error_small
mxl_melt_tomato$ME[23:44] <- mxl_tomato_compare$Margin_of_error_big


ggplot(data=mxl_melt_tomato, aes(x=Coefficent, y=abs(value), fill=variable)) +
  geom_bar(stat="identity",  position='dodge', width = 0.9) +
  geom_errorbar(aes(x=Coefficent, ymin=abs(value)-ME, ymax=abs(value)+ME), width=0.3, position=position_dodge(0.8)) +
  ylab("Absolute Value") +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  scale_fill_brewer(palette = 13, labels = c("Small", "Big"), name="Tomato") +
  theme(legend.position = c(0.9, 0.85))

ggsave("Figure_revision/tomato.png", dpi = "print",  width = 10.5, height = 7.5)


```



#latent class analysis





```{r clogittables, results='asis'}

clmodelsWTP_tex <- models_tex[c("clog_allsamples",  "clog_split_notext" , "clog_split_env"  ,  "clog_split_ind") ]

htmlreg(l = clmodelsWTP_tex , file = "tables/clogit.doc" ,
        custom.model.names = c("Full Sample", "No Text", "Environment" , "Industry") ,  caption = "Results from Infotext Splits" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )

screenreg(l = clmodelsWTP_tex ,
          caption = "Results from Infotext Splits" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )
```



```{r resultsmixedlogit, results='asis'}

mixmodelsWTP_tex <- models_tex[c("mixlog_allsamples",  "mixlog_split_notext" , "mixlog_split_env"  ,  "mixlog_split_ind") ]

htmlreg(l = mixmodelsWTP_tex , file = "tables/mixlogit.doc" ,
        custom.model.names = c("Full Sample", "No Text", "Environment" , "Industry") ,  caption = "Results from Infotext Splits with mixed logit models" , single.row = T  , 
        
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )

screenreg(l = mixmodelsWTP_tex ,
          caption = "Results from Infotext Splits mixedlogit" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )
```

```{r resultsmixedsplitint, results='asis'}

mixlogit_scriptint_tex <- models_tex[["mixlog_scriptint"]]

splitit <-function (select, listobj) {
  
  t<- listobj
  
cells <-grep(select,t@coef.names)  
  
t@coef.names <- t@coef.names[cells]
t@coef <- t@coef[cells]
t@se <- t@se[cells]
t@pvalues <- t@pvalues[cells]
return(t)  

}



intmodel_split <- purrr::map(c("mean","sd", "Info2","Info3"), splitit,mixlogit_scriptint_tex)


htmlreg(l = intmodel_split , file = "tables/mixlogitintsplit.doc" ,
          caption = "Results from mixed logit model with interactions of information treatments" , single.row = T  , 
        
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )

screenreg(l = intmodel_split ,
          caption = "Results from mixed logit model with interactions of information treatments" , single.row = T  , 
        custom.note = "***p < 0.001; **p < 0.01; *p < 0.05 Standard Errors in Brackets" , center = TRUE, doctype = FALSE )
```


```{r ztest}



z.envXind <- apollo_ztest(models[["mixlog_split_env"]],models[["mixlog_split_ind"]])

z.envXnotext <- apollo_ztest(models[["mixlog_split_env"]],models[["mixlog_split_notext"]])


z.notextXind <-apollo_ztest(models[["mixlog_split_notext"]],models[["mixlog_split_ind"]])


# apollo_ztest(models[["clog_split_env"]],models[["clog_split_ind"]])
# 
# apollo_ztest(models[["clog_split_env"]],models[["clog_split_notext"]])
# 
# 
# apollo_ztest(models[["clog_split_notext"]],models[["clog_split_ind"]])


ztest.pvals <- z.envXind %>% 
  tibble::rownames_to_column() %>% 
  bind_cols(z.envXnotext,z.notextXind ) %>% 
  select(Attribute = rowname,EnvXind = p_value...9 , EnvXnotext = p_value...17, notextXind = p_value...25)

flextable(ztest.pvals,) %>% colformat_double(digits = 3) %>% save_as_docx(path = "tables/ztest.docx")


```








